Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-19 DGMM2025/paper.tex
Update biblio
Working on intro

    Visibility is a fundamental concept in computational geometry and digital topology, with applications ranging from computer vision to geometric modeling.
    In this work, we explore visibility through the lens of chord tangency, introducing a novel approach that builds on discrete geometric structures.
    Our framework leverages the discrete setting of and cell complexes, providing a rigorous foundation for analyzing visibility properties in digital spaces.

>>>>

    Visibility is a fundamental concept in computational geometry and
    digital topology, with applications ranging from computer vision
    (identifying occlusions) to geometric modeling (feature detection, geodesics)
    and computer graphics (path tracing, shadowmap). Visibility within
    polygons in the plane has been extensively studied in the
    litterature \cite{ghosh:2007-book} and is still studied in higher
    dimensional spaces \cite{orourke:2017-book}. The general problem
    has a high complexity. For instance, the 3d visibility complex
    between $n$ spheres and occluding spheres has a complexity
    $O(n^4)$ \cite{durand:2002-tog}. Exact 3d visibility between
    polygons and occluding polygons is often casted into 5d Euclidean
    space derived from Plücker space \cite{nirenstein:2002-ewr}, which
    nicely represents 3d lines and their respective positions. The
    computational cost remains high even with decomposition into
    coarse cells for speed up (several days of computation for a
    million triangles at the time).

    To increase efficiency, several authors have proposed to cast the
    visibility problem into a digital space, generally $\Z^3$ or its
    decomposition into cubical cells. Visibility is simplified as the
    problem if there is a connected digital straight line joining a
    pair of cells without occluding cell(s) (e.g. Soille
    \cite{soille:1994-prl} uses Bresenham line segments). Coeurjolly
    \emph{et al.} \cite{coeurjolly:2004-prl} uses a non-symmetric
    visibility definition and preimage computations to speed up that
    kind of algorithms. Chica \cite{chica:2008-spm} uses a half-cell
    erosion of the complementary space and Bresenham straight lines to
    decide visibility.

    We propose an algorithm that solves the following visibility
    problem: given a digital set $X \subset \Z^d$, two points $p,q$ of
    $X$ are \emph{visible} whenever the Euclidean straight line
    segment $\lbrack p,q \rbrack$ is never at $\infty$-distance
    greater or equal to $1$ from $X$.

    (Work in progress)

    Visibility is a fundamental concept in computational geometry and digital topology, with applications ranging from computer vision to geometric modeling and computer graphics.
    In this work, we explore visibility through the lens of chord tangency, introducing a novel approach that builds on discrete geometric structures.
    Our framework leverages the discrete setting of and cell complexes, providing a rigorous foundation for analyzing visibility properties in digital spaces.
